\section{Testing and Performance Evaluation of the TrueNAS Server}

This section delves into a crucial phase of our internship project, where we conducted thorough testing and performance evaluation of the TrueNAS server. Our goal was to ensure that the server could efficiently perform key functions, including serving as an extra storage solution for computers through Samba shares. These shares allow the server to mount as a network drive, providing additional storage to computers on the same local network.

\subsection{Assessing File Sharing Capabilities}

Our initial focus was on evaluating the server's file sharing capabilities, a fundamental aspect of data management. Specifically, we aimed to ensure that the TrueNAS server could function as extra storage for computers on the local network. To achieve this, we configured Samba shares, enabling the server to mount as a network drive on other computers. This setup facilitated seamless file sharing and provided valuable additional storage capacity to computers within the same local network.

\subsection{Virtual Machine Management}

Subsequently, we explored virtual machine management, which is crucial for efficient resource allocation and multitasking. We created a virtual environment within the server, allowing it to run multiple virtual machines (VMs) simultaneously. This capability was vital as it enabled the server to handle various tasks concurrently, similar to a chef managing multiple dishes in a busy kitchen.

\subsection{Integration of Supplementary Plugins}

To enhance the server's capabilities further, we introduced supplementary plugins. These additional tools acted as power-ups, aiding functions like file compression, security enhancements, and server performance monitoring. It was imperative that these plugins seamlessly integrated with the server without causing sluggishness or instability. While some plugins, such as Nextcloud and Plex, were tested for potential future use, they were not incorporated into the final product.

\subsection{Collaborative Problem Solving}

Throughout the testing phase, we encountered challenges that required collective problem-solving. We addressed issues such as relatively slow network connections, resource management to prevent virtual machines from overconsuming computing resources, and fine-tuning the performance of the additional plugins. Our teamwork was essential in resolving these challenges effectively.

\subsection{Validation of Success}

Upon the completion of these comprehensive tests and evaluations, we confidently assert that the TrueNAS server serves as an effective extra storage solution through its Samba shares functionality. It excels in vital functions such as file sharing, virtual machine management, and the integration of supplementary tools to enhance performance and utility. The server is poised to excel in critical tasks, acting as a dependable asset in data management endeavors.

In summary, our testing and performance evaluation confirm that the TrueNAS Server is not only reliable but also capable of serving as additional storage for computers through Samba shares. Its strong performance and versatility make it an invaluable addition to the organization's data management toolkit.
