\subsection{Building a nextcloud server}
This subsection chronicles a significant project undertaken during the internship, focusing on the creation of a Nextcloud server using plugins within the TrueNAS CORE environment. The objective was to establish a secure and user-friendly cloud storage solution, leveraging the power of TrueNAS plugins to simplify the deployment process.

The project began with the installation of the Nextcloud plugin within the TrueNAS CORE system. The plugin, designed to encapsulate the Nextcloud application and its dependencies, streamlined the setup process and alleviated the complexities associated with manual installations. The plugin's user-friendly interface facilitated the configuration of essential parameters, such as storage location, user accounts, and access controls.

Once the Nextcloud plugin was operational, the focus shifted to integrating additional plugins to enhance the server's functionality. Plugins related to data encryption, backup, and monitoring were selected and configured to complement the core Nextcloud application. The selection process was guided by the need to strike a balance between security, performance, and user experience.

Testing constituted a pivotal phase of the project. The server's responsiveness, data synchronization across devices, and security protocols were evaluated. Collaborative efforts were invested in stress testing the system under varying loads and simulating scenarios to ensure data integrity and availability.

Challenges encountered during the project included fine-tuning plugin configurations for optimal performance, addressing compatibility issues among plugins, and ensuring a seamless user experience. These challenges were met with innovative solutions, technical expertise, and effective collaboration within the team.

The successful outcome of the project resulted in the establishment of a functional Nextcloud server within the TrueNAS CORE ecosystem. This accomplishment underscored the versatility of TrueNAS plugins in simplifying complex setups while offering a comprehensive suite of features. The integration of additional plugins enhanced the server's security, data management capabilities, and adaptability, aligning with the organization's commitment to providing robust, user-centric solutions.
