\section{Testing the truenas server}
This subsection presents a crucial phase of the internship project, focusing on the rigorous testing of the TrueNAS server's multifaceted functionalities. The server's capabilities were put to the test through the assessment of Samba shares, virtual machine management, and the integration of additional plugins for enhanced performance and utility.

The testing process commenced with the evaluation of Samba shares, ensuring seamless file sharing and access across diverse platforms. Samba configurations were fine-tuned to optimize performance and security. The server's compatibility with various operating systems and devices was tested, ensuring a user-friendly and accessible file-sharing experience.

The next facet of testing involved the deployment and management of virtual machines (VMs). Virtualization technologies were leveraged to create, configure, and monitor multiple VMs within the TrueNAS server environment. The performance of these VMs was evaluated under varying workloads, testing the server's ability to allocate resources efficiently.

Furthermore, additional plugins were integrated into the server ecosystem to extend its functionality. Plugins for features such as data compression, encryption, and monitoring were tested for their impact on performance, stability, and ease of use. The interplay between plugins and the core server functionalities was carefully examined, validating the overall system's stability.

Challenges encountered during testing included network latency, resource contention among virtual machines, and fine-tuning plugin configurations for optimal performance. Collaborative efforts among team members and consultation with mentors played a vital role in troubleshooting and optimizing the server's performance.

The successful testing phase demonstrated the TrueNAS server's versatility and reliability across diverse scenarios. From providing robust file-sharing capabilities to effectively managing virtualized environments and incorporating supplementary plugins, the server emerged as a comprehensive solution catering to a spectrum of data management needs. This phase underscored the significance of comprehensive testing in validating the server's readiness for real-world deployment.
