\section{Summary}

In culmination, the internship has been a transformative and multifaceted experience that has provided a comprehensive understanding of various aspects of the field. Through a diverse array of projects, ranging from technical configurations to innovative designs, the internship has imparted invaluable skills, insights, and collaborative aptitude.

The project involving the configuration of a gaming server stands as a testament to the intricate nature of hardware integration and resource management. By configuring dual GPUs, dual motherboards, dual power supplies, and a single CPU, the project highlighted the complexities of orchestrating high-performance computing systems while optimizing power and cooling considerations. The process underscored the significance of meticulous hardware selection, fine-tuning BIOS settings, and rigorous stress testing to ensure stability and consistent performance.

The amalgamation of Autodesk Fusion 360 and Blender for the design of a computer case exhibited the dynamic interplay between parametric modeling precision and artistic expression. The creative journey of transforming initial sketches into a refined digital prototype showcased the power of iterative design, culminating in a harmonious balance between aesthetics and functionality.

Furthermore, the network configuration project involving a Cisco switch, MikroTik router, and LAN underscored the pivotal role of seamless connectivity in facilitating efficient data access to the NAS system. By meticulously configuring VLANs, routing protocols, and firewall rules, the project demonstrated the ability to create a robust and secure network infrastructure that enhances data transfer speed and accessibility.

The creation of a Nextcloud server with plugins within the TrueNAS CORE environment exemplified the significance of integrative solutions in catering to diverse user needs. The incorporation of supplementary plugins for encryption, backup, and monitoring showcased the adaptability of the system to accommodate an array of functionalities, augmenting both security and user experience.

The utilization of e-waste components for the construction of a TrueNAS server presented an innovative and sustainable approach to technology utilization. By repurposing discarded electronic components, the project embodied ethical e-waste management practices while contributing to the organization's environmental initiatives.

Collectively, these projects have cultivated a multifaceted skill set that encompasses technical prowess, creative problem-solving, collaboration, and adaptability. As the internship concludes, the gained knowledge and experiences will undoubtedly serve as the foundation for continued growth and success in the dynamic realm of technology.
