\addcontentsline{toc}{chapter}{Acknowledgement}

I extend my heartfelt gratitude to Allah the Almighty for granting me the strength and ability to successfully complete this internship report.

My deepest thanks go to my mother and siblings for their unwavering support and encouragement throughout my internship journey. Their steadfast belief in my abilities gave me the resilience to overcome challenges and excel during my internship.

I am sincerely appreciative of all those who contributed to the successful completion of my internship and the preparation of this report.

Foremost, I owe a debt of gratitude to my internship supervisor, \textbf{Dr. Edwin Mugume}, for his invaluable guidance, mentorship, and insights that shaped my understanding and skills. I am equally thankful to my internship trainer, \textbf{Mr. Uding}, for his constant support and motivation during my internship.

I express my deep appreciation to the entire team at \textbf{NetLabs} and \textbf{G-Nex} for welcoming me and providing me with the opportunity to participate in their projects and initiatives. The experiences I gained, particularly in pc building and networking, were truly enriching and educational.

I also want to acknowledge the faculty members and staff at \textbf{Makerere University College of Engineering, Design, Art, and Technology} for their unwavering support and encouragement during my internship. The knowledge and skills I acquired during my academic studies played a pivotal role in my ability to contribute effectively during this internship.

Lastly, I want to express my heartfelt thanks to my family and friends for their constant encouragement, motivation, and unwavering belief in my abilities. Your support provided me with the strength to surmount challenges and excel during my internship.

This internship experience has been invaluable in shaping my professional growth, and I am genuinely thankful for all the opportunities I have received.
