\addcontentsline{toc}{chapter}{Preface}

This report serves as documentation of my industrial training experience at Netlabs UG during the period of \textbf{18/6/2023 to 19/6/2023}. It represents the culmination of my efforts, learning, and contributions during this internship.

The internship provided me with invaluable hands-on experience in the field of electrical and computer engineering, allowing me to apply the theoretical knowledge acquired during my academic journey to real-world scenarios. It was an opportunity to work alongside experienced professionals, engage in diverse projects, and immerse myself in the dynamic world of technology.

Throughout this report, I have endeavored to provide a comprehensive account of the various projects and activities undertaken during my internship. These experiences have not only enriched my technical skills but have also fostered personal and professional growth.

I would like to express my gratitude to \textbf{Dr. Edwin Mugume}, my internship supervisor, for his unwavering support and guidance throughout this journey. His mentorship has been instrumental in shaping my understanding of the field and enhancing my problem-solving abilities.

Additionally, I am thankful to the entire team at Netlabs for their warm welcome, collaboration, and the wealth of knowledge they shared with me. The supportive environment and collective expertise made this internship a truly enriching experience. I also thank the team at Gnex for their support in the manufacturing process.

I hope that this report not only serves as an account of my internship but also as a resource for future students and professionals seeking insights into the realm of electrical and computer engineering. It is my aspiration that the knowledge and experiences shared herein contribute to the advancement of this field.

\begin{flushright}
    Sincerely, \\
    Shawal Mbalire \\
    21/U/0851 \\
    \today \\
    Kampala, Uganda
\end{flushright}
