In this chapter, we offer an in-depth exploration of the multitude of tasks, diverse projects, and significant responsibilities that defined our enriching internship experience at NetLab!UG. These experiences spanned a wide spectrum of activities, each thoughtfully contributing to the overarching objectives of the projects while concurrently providing invaluable learning opportunities. Our narrative delves into the granular specifics of these assignments, illuminating the methodologies meticulously employed to execute them effectively.

These real-world experiences were not devoid of challenges; in fact, they presented opportunities for growth and problem-solving. Within this narrative, we candidly discuss the multifaceted challenges encountered during our tenure, offering transparency in our exploration. Furthermore, we articulate the strategic solutions devised to triumph over these hurdles, showcasing adaptability and resilience in the face of adversity.

The essence of this section lies in its ability to offer readers profound insights into the practical application of the skills and knowledge we had diligently accumulated in our academic pursuits. As we recount these endeavors, we underscore the symbiotic relationship between theoretical understanding and hands-on proficiency. Moreover, our recounting serves as a testament to the meaningful contributions we made towards the realization of key projects and initiatives within the organization.

Through this comprehensive exposition, we endeavor to convey not only the breadth and depth of our experiences but also the lasting impact of our efforts on NetLab!UG's mission and objectives. The projects undertaken were not mere tasks; they were pivotal milestones in our professional journey, offering transformative lessons and fostering a deep sense of purpose.
\input{chapters/workdone/1building.tex}
\input{chapters/workdone/2testing.tex}
\input{chapters/workdone/3truenas.tex}
\input{chapters/workdone/4trunastest.tex}
\input{chapters/workdone/5nextcoud.tex}
\input{chapters/workdone/6rout.tex}
\input{chapters/workdone/7_3d.tex}
\input{chapters/workdone/8motiv.tex}
\input{chapters/workdone/9gaming.tex}
\input{chapters/workdone/10summary.tex}










